### 2025-04-08 Paper.tex
add changes

	We also used whisper-timestamped, which is an extension of whisper and provides more efficient and accurate word timestamps. Whisper-timestamped uses a Dynamic Time Warping approach, which allows it to create word timestamps and a more accurate estimation on speech segments. As a result, the estimated start and end times of speech segments are more precise. Another advantage over the base model is that Whisper Timestamped can process longer files \cite{Andreyev2025}.

@@

	To include more data and improve model performance, we additionally included two live albums in our dataset. As many segments contained screaming from the audience, we went through them and cut out unwanted parts manually with Praat, a tool for speech analysis and phonetic research.

>>>>

	We also used whisper-timestamped, which is an extension of whisper and provides more efficient and accurate word timestamps. Whisper-timestamped uses a Dynamic Time Warping approach, which allows it to create word timestamps and a more accurate estimation on speech segments. As a result, the estimated start and end times of speech segments are more precise. Another advantage over the base model is that whisper-timestamped can process longer files \cite{Andreyev2025}.

@@

	To include more data and improve model performance, we additionally included two live albums in our dataset. As many segments contained screaming from the audience, we went through them and cut out unwanted parts manually with Praat, a tool for speech analysis and phonetic research \cite{BoersmaND}.
